\documentclass[12pt,a4paper]{article}

% ---------- Packages ----------
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{parskip} % space between paragraphs, no indent
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{setspace}
\usepackage{fontawesome5} % icons
\usepackage{fancyhdr}
\usepackage{titlesec}

% ---------- Formatting ----------
\setstretch{1.08}
\titleformat{\section}{\large\bfseries}{}{0pt}{}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\rfoot{\thepage}

% ---------- Your info (from CV) ----------
\newcommand{\Name}{Sheng-Hsun Chang}
\newcommand{\Email}{\href{mailto:ic046262@gmail.com}{ic046262@gmail.com}}
\newcommand{\Phone}{+886-903-086-553}
% Replace with your actual URLs:
\newcommand{\GitHub}{\href{https://github.com/}{GitHub}}
\newcommand{\LinkedIn}{\href{https://www.linkedin.com/}{LinkedIn}}

\begin{document}

% ---------- Header ----------
{\LARGE \textbf{\Name}}\\
Undergraduate, Electrical Engineering, National Taiwan University\\
\vspace{2pt}
\faEnvelope\ \Email \quad
\faPhone\ \Phone \quad
\faGithub\ \GitHub \quad
\faLinkedin\ \LinkedIn

\vspace{14pt}

% ---------- Date + Recipient ----------
\textbf{Date:} \today\\
\textbf{To:} Hiring Team, Huld\\
\textbf{Subject:} Motivation Letter --- Software Engineering Intern (Jun 15 -- Aug 31, 2026)


\vspace{10pt}
\hrule
Dear Hiring Team:

I am writing to apply for the Software Engineering Intern position at Huld. 
I am currently an undergraduate student pursuing a degree in Electrical Engineering at 
National Taiwan University, where I have developed a strong academic foundation alongside 
hands-on experience in software and system-oriented projects. I'm
eager to contribute to Huld while continuing to 
grow as a software engineer in an agile development environment.

My project experience in reinforcement learning has equipped me with a solid programming foundation. 
During the RL project, despite the project scope being revised twice, I actively collaborated with my teammates to identify and resolve the emerging challenges. Through this process, I developed strong proficiency in Python, PyTorch, and Stable Baselines3, 
as well as hands-on experience debugging complex learning systems. 
This experience strengthened my ability to decompose ambiguous problems into concrete, manageable objectives and address them iteratively. 
Ultimately, our team achieved \textbf{third place} in the final project presentation among 30 teams, most of which were composed of \textbf{graduate students}.

Besides course projects, I also participated in the NTUEE Light Dance project, 
a large-scale program which integrates software development, embedded systems, 
and real-world performance constraints. I was involved in the design of wearable lighting costumes, 
where I had to balance wearability with system stability and reliability. Also, I participated in the follow-up 
improvement for the ESP32-based real-time communication system. During the event, I got to know how to deliver 
solutions under physical constraints.

I am also a member of the Industry Department within the student association.
By conducting regular interviews with senior students and professors, I gained a deeper understanding of current 
industry trends while honing my presentation and communication skills. In sharing these insights with freshmen, 
I further developed my ability to convey complex concepts clearly and accessibly.

To conclude, I would like to contribute my technical skills and collaborative experience to the Software Engineering Internship at Huld. I would appreciate the opportunity to contribute to your development team while continuing to learn from experienced engineers in a challenging environment. Thank you for your time and consideration.


Sincerely,\\
\vspace{10pt}
\Name


\end{document}