\documentclass[12pt,a4paper]{article}

% ---------- Packages ----------
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{parskip} % space between paragraphs, no indent
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{setspace}
\usepackage{fontawesome5} % icons
\usepackage{fancyhdr}
\usepackage{titlesec}

% ---------- Formatting ----------
\setstretch{1.08}
\titleformat{\section}{\large\bfseries}{}{0pt}{}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\rfoot{\thepage}

% ---------- Your info (from CV) ----------
\newcommand{\Name}{Sheng-Hsun Chang}
\newcommand{\Email}{\href{mailto:ic046262@gmail.com}{ic046262@gmail.com}}
\newcommand{\Phone}{+886-903-086-553}
% Replace with your actual URLs:
\newcommand{\GitHub}{\href{https://github.com/}{GitHub}}
\newcommand{\LinkedIn}{\href{https://www.linkedin.com/}{LinkedIn}}

\begin{document}

% ---------- Header ----------
{\LARGE \textbf{\Name}}\\
Undergraduate, Electrical Engineering, National Taiwan University\\
\vspace{2pt}
\faEnvelope\ \Email \quad
\faPhone\ \Phone \quad
\faGithub\ \GitHub \quad
\faLinkedin\ \LinkedIn

\vspace{14pt}

% ---------- Date + Recipient ----------
\textbf{Date:} \today\\
\textbf{To:} Hiring Team, Learning Robots\\
\textbf{Subject:} Motivation Letter --- AI \& Robotics Intern (Jun 15 -- Aug 31, 2026)


\vspace{10pt}
\hrule
Dear Hiring Team:

I am writing to apply for the AI \& Robotics Intern position at Learning Robots. 
I am currently an undergraduate student pursuing a degree in Electrical Engineering at 
National Taiwan University, where I have developed a strong academic foundation alongside 
hands-on experience in software and system-oriented projects. I am particularly drawn to 
Learning Robots' mission of making AI accessible through robotics and interactive educational tools.

I am currently involved in Professor Shao-Hua Sun's Robot Learning Laboratory, where I
regularly attend group meetings and research discussions focused on reinforcement learning
and robot learning. Through these sessions, I have been exposed to how AI models are
designed, analyzed, and evaluated in the context of robotic systems, and how experimental
results are interpreted and refined through iteration.

My project experience in reinforcement learning has equipped me with a solid programming foundation. 
During the RL project, despite the project scope being revised twice, I actively collaborated with my teammates to identify and resolve the emerging challenges. Through this process, I developed strong proficiency in Python, PyTorch, and Stable Baselines3, 
as well as hands-on experience debugging complex learning systems. 
This experience strengthened my ability to decompose ambiguous problems into concrete, manageable objectives and address them iteratively. 
Ultimately, our team achieved \textbf{third place} in the final project presentation among 30 teams, most of which were composed of \textbf{graduate students}.

Beyond technical skills, I am also teaching IT and basic programming to junior high school students during winter breaks.
This experience requires me to select appropriate teaching materials, translates complex concepts into digestible lessons,
and designs interactive activities to engage students. Through teaching, My skills in visualization, communication, 
and adapting explanations to different audiences are significantly enhanced.

To conclude, I would like to contribute my technical skills and collaborative experience to the AI \& Robotics Intern position at Learning Robots. 
I would appreciate the opportunity to contribute to your development team while continuing to learn from experienced engineers in a challenging environment. 
Thank you for your time and consideration.


Sincerely,\\
\vspace{10pt}
\Name


\end{document}